---
title: "04. Benchmark"
output: 
  html_document:
    smart: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r message=FALSE, warning=FALSE}

library(magrittr)
library(dplyr)
library(ggplot2)

```

```{r}

load(here::here('Data', 'Processed_data', 'augmented_descriptors.Rdata'))
load(here::here('Data', 'filtered_features.Rdata'))

source(here::here('R', 'Analysis', 'aux_predictions.R'))
source(here::here('R', 'Analysis', 'aux_experiments.R'))
source(here::here('R', 'Analysis', 'aux_metrics.R'))

```



```{r}

meta_vars  <- c('Degradation_stage', 'Load', 'Test_ID', 'Origin', 'Segment', 'Repetition')

seed <- 666

Load_value <- c(40, 20)

```


# Baseline

What is an acceptable Kappa value for the diagnosis algorithm?

## 3 labels (Spalling / Lubrication / Nominal)


```{r}

case1 <- matrix(c(400,0,50,0,100,0,0,0,0), ncol = 3, byrow = TRUE) # Every fault categorised as spalling
case1

Kappa(case1) # Every fault categorised as spalling




```

## 2 labels (Spalling / Lubrication)


```{r}

case2 <- matrix(c(400,0,100,0), ncol = 2, byrow = TRUE) # Every fault categorised as spalling
case2

Kappa(case2) # Every fault categorised as spalling

sum(diag(case2) )/sum(case2)

```


```{r}

case3 <- matrix(c(400,0,25,75), ncol = 2, byrow = TRUE) # Half lubrication as spalling
case3

Kappa(case3) # Every fault categorised as spalling



```

```{r}

simulate_missclassification <- function(miss_lub_prop, lub = 100, point = 400){
  
Kappa(matrix(c(400,0, lub*miss_lub_prop,lub*(1-miss_lub_prop)), ncol = 2, byrow = TRUE))
  
}

sapply(c(0.03, 0.05, 0.15, 0.25), FUN = simulate_missclassification)





```

# Real data using chronology with all loads and filtered features


```{r}



train_idx <- with(descriptors, Origin == 'Real' & Load %in% Load_value )

test_idx <- with(descriptors, Origin == 'Real' & Load %in% Load_value )

train_test <- data_case_filter(descriptors, train_cases = train_idx, test_cases = test_idx, features = final_features, remove_vars = meta_vars, show_validity = TRUE)



seeds <- seq(1:10)*seed

experiments <- lapply(seeds, FUN = create_experiment, 
                     train_test = train_test,  
                     remove_vars = meta_vars,
                     target_var = 'Test_ID', 
                     scale_data = TRUE,
                     train_prop = 0.75, 
                     grouping_vars = meta_vars)

# With chronology 

predictions <- lapply(experiments, predict_lda)

R_f_f_L4020 <- get_metrics(predictions)

R_f_f_L4020$cohen_Kappa %>% mean()

# With chronology

predictions <- lapply(experiments, predict_majority_lda)

R_f_f_L4020_chronology <- get_metrics(predictions)

R_f_f_L4020_chronology$cohen_Kappa %>% mean()

```



# Synthetic data and nominal real cases using chronology with all loads and filtered features


```{r}



train_idx <- with(descriptors, (Origin == 'Synthetic' | (Origin == 'Real' & Test_ID =='train')) & Load %in% Load_value )

test_idx <- with(descriptors, Origin == 'Real' & Load %in% Load_value )

train_test <- data_case_filter(descriptors, train_cases = train_idx, test_cases = test_idx, features = final_features, remove_vars = meta_vars, show_validity = TRUE)



seeds <- seq(1:10)*seed

experiments <- lapply(seeds, FUN = create_experiment, 
                     train_test = train_test,  
                     remove_vars = meta_vars,
                     target_var = 'Test_ID', 
                     scale_data = TRUE,
                     train_prop = 0.75, 
                     grouping_vars = meta_vars)

predictions <- lapply(experiments, predict_lda)

S_f_f_L4020 <- get_metrics(predictions)

S_f_f_L4020$cohen_Kappa %>% mean()

predictions <- lapply(experiments, predict_majority_lda)

S_f_f_L4020_chronology <- get_metrics(predictions)

S_f_f_L4020_chronology $cohen_Kappa %>% mean()

```


# Real data binary with all loads and filtered features


```{r}



train_idx <- with(descriptors, Origin == 'Real' & Load %in% Load_value & Test_ID %in% c('lub', 'point') )

test_idx <- with(descriptors, Origin == 'Real' & Load %in% Load_value & Test_ID %in% c('lub', 'point'))

train_test <- data_case_filter(descriptors, train_cases = train_idx, test_cases = test_idx, features = final_features, remove_vars = meta_vars, show_validity = TRUE)



seeds <- seq(1:10)*seed

experiments <- lapply(seeds, FUN = create_experiment, 
                     train_test = train_test,  
                     remove_vars = meta_vars,
                     target_var = 'Test_ID', 
                     scale_data = TRUE,
                     train_prop = 0.75, 
                     grouping_vars = meta_vars)


predictions <- lapply(experiments, predict_lda)

R_f_f_L4020_binary <- get_metrics(predictions)

R_f_f_L4020_binary$cohen_Kappa %>% mean()

# Chronology

predictions <- lapply(experiments, predict_lda)

R_f_f_L4020_binary_chronology <- get_metrics(predictions)

R_f_f_L4020_binary_chronology$cohen_Kappa %>% mean()

```

# Syn data real nominal binary with all loads and filtered features

```{r}

train_idx <- with(descriptors, Origin == 'Synthetic' & Load %in% Load_value & (Test_ID %in% c('lub', 'point')))

test_idx <- with(descriptors, Origin == 'Real' & Load %in% Load_value & (Test_ID %in% c('lub', 'point')) )

train_test <- data_case_filter(descriptors, train_cases = train_idx, test_cases = test_idx, features = final_features, remove_vars = meta_vars, show_validity = TRUE)



seeds <- seq(1:10)*seed

experiments <- lapply(seeds, FUN = create_experiment, 
                     train_test = train_test,  
                     remove_vars = meta_vars,
                     target_var = 'Test_ID', 
                     scale_data = TRUE,
                     train_prop = 0.75, 
                     grouping_vars = meta_vars)



predictions <- lapply(experiments, predict_lda)

S_f_f_L4020_binary <- get_metrics(predictions)

S_f_f_L4020_binary$cohen_Kappa %>% mean()

# Chronology

predictions <- lapply(experiments, predict_majority_lda)

S_f_f_L4020_binary_chronology <- get_metrics(predictions)

S_f_f_L4020_binary_chronology$cohen_Kappa %>% mean()


```
# Graphs

```{r}

multilabel_kappa <- rbind(
                        R_f_f_L4020$cohen_Kappa,
                        R_f_f_L4020_chronology$cohen_Kappa,
                        S_f_f_L4020$cohen_Kappa,
                        S_f_f_L4020_chronology$cohen_Kappa
                          )


binary_kappa <- rbind(
                        R_f_f_L4020_binary$cohen_Kappa,
                        R_f_f_L4020_binary_chronology$cohen_Kappa,
                        S_f_f_L4020_binary$cohen_Kappa,   
                        S_f_f_L4020_binary_chronology$cohen_Kappa
                        )

```

### Faults together

```{r }

multilabel_k <- t(multilabel_kappa) %>% 
  as.data.frame() %>% 
  tidyr::gather(., key = 'Test', 'value') %>% 
  mutate(Test = forcats::fct_relevel(Test,   paste('V', 1:4, sep = '')   ) ) %>% 
  mutate(Test = forcats::fct_recode(Test,   "Real data" = 'V1', "Real data \nusing \nchronology" = 'V2', "Synthetic" = 'V3', "Synthetic \nusing \nchronology" = 'V4') ) %>% 
  ggplot(., aes(x= Test, y = value)) + 
  geom_boxplot() +
  geom_hline(yintercept = Kappa(case1), color = 'red', linetype = 'dashed') +
  theme_minimal() +
  ylab('Kappa') +
  xlab('') +
  annotate(geom = 'text', x = 3.2, y = 0.715, label = '\"All-Spalling\"\n scenario', color = 'red', fill = 'red', size = 3) +
  scale_y_continuous(limits=c(0.5, 0.8)) +
  coord_flip()
  

multilabel_k


multilabel_k %>% 
  cowplot::save_plot(plot = .,
                     filename = here::here('figures', 'benchmark_multilabel_boxplot_kappa.png'),
                     dpi = 450,
                     bg = 'transparent'
                     )

```

```{r}

prop_missclasified <- c(0.03, 0.05, 0.15, 0.25)
resulting_kappa <- sapply(prop_missclasified, FUN = simulate_missclassification)
grouping_var <- 1:length(prop_missclasified)
text_label <- paste0(prop_missclasified*100, '%')

baseline_table <- data.frame(prop_missclasified,  resulting_kappa, grouping_var, text_label )

binary_k <- t(binary_kappa) %>% 
  as.data.frame() %>% 
  tidyr::gather(., key = 'Test', 'value') %>% 
  mutate(Test = forcats::fct_relevel(Test,   paste('V', 1:4, sep = '')   ) ) %>% 
  mutate(Test = forcats::fct_recode(Test,   "Real data" = 'V1', "Real data \nusing \nchronology" = 'V2', "Synthetic" = 'V3', "Synthetic \nusing \nchronology" = 'V4') ) %>% 
  {ggplot() + 
  geom_boxplot(data = ., aes(x= Test, y = value)) +
  geom_hline(baseline_table, yintercept = resulting_kappa, color = 'red', linetype = 'dashed' ) +
  geom_text(data = baseline_table, aes(x = 1.2, y = resulting_kappa-0.005 , label = text_label, color = 'red', fill = 'red'), size = 3 ) +
  theme_minimal() +
  ylab('Kappa') +
  scale_y_continuous(limits=c(0.8, 1.00)) +
      xlab('') +
      theme(legend.position = 'none') +
      coord_flip()
  }
  

binary_k$layers <- c(binary_k$layers, binary_k$layers[[1]])
binary_k

binary_k %>% 
    cowplot::save_plot(plot = .,
                     filename = here::here('figures', 'benchmark_binary_boxplot_kappa.png'),
                     dpi = 450,
                     bg = 'transparent'
                     )

```


```{r}

multi_binary_combined <- cowplot::plot_grid(
                                             multilabel_k,
                                             binary_k + theme(axis.text.y = element_blank()),
                                             labels = c("a)", "b)")
                                            ) 

multi_binary_combined

multi_binary_combined %>% 
      cowplot::save_plot(plot = .,
                     filename = here::here('figures', 'benchmark_combined_boxplot_kappa.png'),
                     dpi = 450,
                     bg = 'transparent'
                     )

```

