---
title: "00_Synthetic _data_validation"
author: "Kerman López de Calle Etxabe"
date: "17/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```


# Visual inspection of synthetised data

This scripts displays the signals that are recreated by the model.


```{r echo=FALSE, message=FALSE, warning=FALSE}

library(magrittr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(factoextra)
library(cowplot)

load(here::here('Data', 'bigdata.Rdata'))


source(here::here('R', 'Pre-processing', '00_Synthetic_data_validation_auxiliars.R'))

```


```{r}

synthetic_files <- dir(here::here('Data', 'Synthetic_data'))

synthetic_files <- synthetic_files [grep('.mat', synthetic_files)]

parsed_files <- parse_mat_files(synthetic_files)

parsed_files <- parsed_files[complete.cases(parsed_files),]

formated_files <- lapply(parsed_files$Sourcefile, 
                         FUN = read_n_add_meta_syn
                         )

formated_files <- do.call('rbind', formated_files)

formated_files %<>% mutate(., Test_ID = 
  case_when(
      ViscousFR>0 &  StartSpalling >= 140 ~ 'lub',
      StartSpalling <140 ~ 'point',
      ViscousFR==0 &  StartSpalling >= 140 ~  'train'
      )
          ) %>% 
group_by(Test_ID, Load, ViscousFR, SpallingFR) %>% 
            mutate(., Degradation_stage = case_when(
                                                      ViscousFR>0 ~ as.character(ViscousFR),
                                                      SpallingFR>0 ~ as.character(SpallingFR),
                                                      TRUE ~ '0'
                                                      )
            ) %>% 
  ungroup()

```


## Loads

The following figure depics the synthetic Current and Position error signals under different loads.


```{r}

load_big <- filter(bigdata, Test_ID == 'train', Motion == 'trapezoidal', Repetition == 1, Segment == 1 )

re_pos_error_by_load <-  load_big %>%
                            mutate(`Load [kg]` = factor(Load)) %>% 
                            ggplot(., aes(STime, Pos_error, colour = `Load [kg]` )) +
                                                  geom_line(size = 0.7, linetype = "dashed") +
                                                  theme_minimal() + 
                                                  xlab('Time [s]') +
                                                  ylab('Position error [mm]') +
                                                  theme(legend.position = 'none') +
                                                  ylim(-5, 5)

re_current_by_load <-  load_big %>%
                            mutate(`Load [kg]` = factor(Load)) %>% 
                            ggplot(., aes(STime, Current, colour = `Load [kg]` )) +
                                                  geom_line(size = 0.7, linetype = "dashed") +
                                                  theme_minimal() + 
                                                  xlab('Time [s]') +
                                                  ylab('Current [A]') +
                                                  theme(legend.position = 'none') +
                                                  ylim(0.2, 1.35)

```


```{r}



current_by_load <- formated_files %>% 
                      filter(Test_ID == 'train') %>% 
                      ggplot(., aes(STime, Current, colour = factor(Load) )) +
                      geom_line(size = 0.7, linetype = "dashed") +
                      theme_minimal() + 
                      xlab('Time [s]') +
                      ylab('Current [A]') +
                      ylim(0.2, 1.35)

pos_error_by_load <- formated_files %>% 
                      filter(Test_ID == 'train') %>% 
                      mutate(`Load [kg]` = factor(Load)) %>% 
                      ggplot(., aes(STime, Pos_error, colour = `Load [kg]` )) +
                      geom_line(size = 0.7, linetype = "dashed") +
                      theme_minimal() + 
                      theme(legend.position = 'bottom') +
                      xlab('Time [s]') + 
                      ylab('Position error [mm]') +
                      ylim(-5, 5)

legenda <- get_legend(pos_error_by_load)

load_effect <- cowplot::plot_grid(
      cowplot::plot_grid( re_current_by_load,
                          re_pos_error_by_load,
                          current_by_load + theme(legend.position = 'none'), 
                          pos_error_by_load + theme(legend.position = 'none'),
                          ncol = 2,
                          labels = c('a)', 'b)', 'c)', 'd)'),
                          hjust = -3.05
                    ),
legenda,
ncol = 1,
rel_heights = c(1,0.15)
)  
  cowplot::save_plot(plot = load_effect, 
                     filename = paste0(here::here('figures'), '/', 'syn_real_signals', '.png' ),
                     dpi = 450,
                     base_aspect_ratio = 2.3,
                     bg= 'transparent'
                     ) 

load_effect
```



## Friction

The following figure depics the lack of lubrication failure with increasing severity.

```{r Friction values}



fake_friction <- formated_files %>% 
  filter((Test_ID == 'train' | Test_ID == 'lub'), Load == 20)

fake_friction <- fake_friction %>% 
  mutate(Test_ID = factor(Test_ID, labels = c('Friction', 'Nominal')),
         ViscousFR = factor(ViscousFR, labels = c('','Very low', 'Low', 'Medium', 'High'))
         )  


friction_current <- ggplot( ) +
                      geom_line(data = fake_friction, aes(STime, Current, colour = interaction(Test_ID, ViscousFR) ), linetype = "dashed") + 
                      theme_minimal() +
                      xlab('Time') +
                      ylab('Current') +
                      labs(color = "")


    
friction_poserror <- ggplot( ) +
                        geom_line(data = fake_friction, aes(STime, Pos_error, colour = interaction(Test_ID, ViscousFR) ), linetype = "dashed")  +
                        theme_minimal() + 
                        xlab('Time') +
                        ylab('Current') +
                        labs(color = "") +
                        theme(legend.position = 'bottom')
                        

legenda <- get_legend(friction_poserror)

friction_fault <- cowplot::plot_grid(
  cowplot::plot_grid(
    {friction_current + theme(legend.position = 'none')},
    {friction_poserror+ theme(legend.position = 'none')},
    labels = c('a)', 'b)')
                     ),
  legenda, 
ncol = 1,
rel_heights = c(1, 0.1)

  ) 

    cowplot::save_plot(plot = friction_fault, 
                     filename = paste0(here::here('figures'), '/', 'friction_fault_signal', '.png' ),
                     dpi = 450,
                     base_aspect_ratio = 2.3,
                     bg= 'transparent'
                     ) 
friction_fault

```



## Spalling

The following figure depics spalling failures with increasing severity.


```{r}


fake_spalling <- formated_files %>% 
  filter((Test_ID == 'train' | Test_ID == 'point'), Load == 20) 
  
  
fake_spalling <- fake_spalling %>% 
                      mutate(Test_ID = factor(Test_ID, labels = c('Spalling', 'Nominal')),
                             SpallingFR = factor(SpallingFR, labels = c('', 'Low', 'Medium', 'High'))
                             )  

current_spalling <-   ggplot(fake_spalling, aes(STime, Current, colour = interaction(Test_ID, SpallingFR) )) +
                            geom_line(size = 0.55,linetype = "dashed") +
                            theme_minimal() + 
                            labs(color = "") +
                            xlab('Time') +
                            ylab('Current') +  
                            theme(legend.position = 'bottom')

poser_spalling <-   ggplot(fake_spalling, aes(STime, Pos_error, colour = interaction(Test_ID, SpallingFR) )) +
                            geom_line(size = 0.55,linetype = "dashed") +
                            theme_minimal() + 
                            labs(color = "") +
                            xlab('Time [s]') +
                            ylab('Position error [mm]') +  
                            theme(legend.position = 'bottom')

legenda <- get_legend(poser_spalling)

spalling_fault <- cowplot::plot_grid(
      cowplot::plot_grid(
        current_spalling + theme(legend.position = 'none'),
        poser_spalling + theme(legend.position = 'none' ),
      labels = c('a)', 'b)')
                        ),
      legenda,
      ncol = 1,
      rel_heights = c(1,0.1)
                    ) 

      cowplot::save_plot(plot = spalling_fault, 
                     filename = paste0(here::here('figures'), '/', 'spalling_fault_signal', '.png' ),
                     dpi = 450,
                     base_aspect_ratio = 2.3,
                     bg= 'transparent'
                     ) 
    
      spalling_fault

```

