---
title: "01.2_Extracted descriptors"
output: 
  html_document:
    smart: false
---

# Extracted descriptors

The steps taken to extract descriptors are shown here visually.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```


```{r Data loading}

load(here::here('Data', 'bigdata.Rdata'))

```


```{r warning=FALSE, message = FALSE}

library(magrittr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(cowplot)
library(ggrepel)

source(here::here('R', 'Pre-processing', '00_Synthetic_data_validation_auxiliars.R'))



```

## Original signals

Originally there are three signals (Setpoint, Position error and Setpoint), each of them contain more than one repetition. However, during the downloading of the data an additional variable indicating the cycle has been added already.  

```{r}

trapezoids <- bigdata %>% filter(Test_ID=='train', Motion == 'trapezoidal', Load == 20, Repetition == 1, between(Segment, 1,2) ) 

plot_grid(
  ggplot(trapezoids, aes(Time, Current)) + geom_line() + theme_minimal(),
  ggplot(trapezoids, aes(Time, Pos_error)) + geom_line() + theme_minimal(),
  ggplot(trapezoids, aes(Time, Setpoint)) + geom_line() + theme_minimal()
)

segment <- bigdata %>% filter(Test_ID=='train', Motion == 'trapezoidal', Load == 20, Repetition == 1, Segment == 1 ) 

```


```{r}

time_var = 'STime'

segment_names <- names(segment)


```

```{r}

segment %<>% 
        mutate(Region = ifelse(Setpoint > 139 & between(STime, 5, 10), 'Extended',
                               ifelse( (Setpoint>0 & Setpoint < 139) & c(0, diff(Setpoint))>0 & between(STime, 1,7), 'Extending',
                                       ifelse( Setpoint < 21, 'Idling',
                                       ifelse((Setpoint>0 & Setpoint < 139) & c(0, diff(Setpoint))<0 & between(STime, 9,15),'Retracting', 'Other'))
                               ) )
        ) 

```

## Dividing the cycle

In order to segment each cycle in smaller processes (Extending, Retracting, Extended and Idling) Setpoint is used.

```{r}

p_seg_divide <- ggplot(segment, aes(STime, Setpoint, colour = Region )) +
                  geom_point() +
                  theme_minimal()

p_seg_divide %>%  
  cowplot::save_plot(plot = .,
                     filename = here::here('figures', 'setpoint_segmentation.png'),
                     dpi = 450,
                     bg = 'transparent'
                     )

  p_seg_divide

```



```{r Measuring indicators and position}


segment_region_length <- sum(segment$Region == 'Retracting')

n_two_third_tail <- round(segment_region_length*2/3) 
n_first_quarter <- round(segment_region_length*1/4)

 retraction <- segment %>% 
                filter(Region == 'Retracting') %>% 
                mutate(
                  Idx = 1:n(), tail_two_thirds =  ifelse(Idx < (n() - n_two_third_tail), FALSE, TRUE)
                  )
 
 
 
 
 indicators  <- retraction %>% 
                  describe(., return_location = TRUE)
 
  
```

# Retraction

With the previous division, it is possible to take the tail and the head of each sub-process and extract the descriptors. 

```{r}

p_ret_cur <-  ggplot() + 
   geom_line(data = retraction, aes(Idx, Current , colour = tail_two_thirds)) +
   geom_point(data = indicators, aes(w_max_current, max_current)) + 
   geom_text_repel(data = indicators, aes(w_max_current, max_current, label = 'Max')) +
   geom_point(data = indicators, aes(w_max_current, max_current)) +
   geom_text_repel(data = indicators, aes(w_min_current, min_current, label = 'Min')) +
   geom_point(data = indicators, aes(w_min_current, min_current)) +
   geom_segment(aes(x = segment_region_length - n_two_third_tail, y = indicators$mean_current, xend = segment_region_length, yend = indicators$mean_current)) +
  geom_text_repel(data = indicators, aes(segment_region_length -n_two_third_tail+3,mean_current + 0.075, label = 'Mean')) + 
  geom_vline(xintercept = n_first_quarter, linetype = 'dashed' ) +
  geom_point(data = indicators, aes(w_overshoot_current, overshoot_current)) +
  geom_text_repel(data = indicators, aes(w_overshoot_current, overshoot_current, label = 'Overshoot')) +
  geom_segment(aes(x = 75, y = indicators$min_current, xend = 75, yend = indicators$max_current), arrow = arrow(length = unit(0.25, "cm"))) +
  geom_segment(aes(x = 75, y = indicators$max_current, xend = 75, yend = indicators$min_current), arrow = arrow(length = unit(0.25, "cm"))) +
  geom_text_repel(data = indicators, aes(72, indicators$min_current-0.05, label = 'Peak value')) +
  theme_minimal() + 
  theme(legend.position = 'none') + 
  xlab('')

p_ret_cur

```




```{r}

p_ret_pose <-  ggplot() + 
   geom_line(data = retraction, aes(Idx, Pos_error , colour = tail_two_thirds)) +
   geom_line(data = retraction[1:n_first_quarter,], aes(Idx, abs(Pos_error)), linetype = 'dashed')  + 
   geom_point(data = indicators, aes(w_max_Pos_error, max_Pos_error)) + 
   geom_text_repel(data = indicators, aes(w_max_Pos_error, max_Pos_error, label = 'Max')) +
   geom_point(data = indicators, aes(w_max_Pos_error, max_Pos_error+0.05)) +
   geom_text_repel(data = indicators, aes(w_min_Pos_error+2, min_Pos_error-0.05, label = 'Min')) +
   geom_point(data = indicators, aes(w_min_Pos_error, min_Pos_error)) +
   geom_segment(aes(x = segment_region_length -n_two_third_tail, y = indicators$mean_Pos_error, xend = segment_region_length, yend = indicators$mean_Pos_error)) + 
  geom_text_repel(data = indicators, aes(segment_region_length -n_two_third_tail+3, mean_Pos_error + 0.1, label = 'Mean')) + 
  geom_vline(xintercept = n_first_quarter, linetype = 'dashed' ) +
  geom_point(data = indicators, aes(w_overshoot_Pos_error, overshoot_Pos_error)) +
  geom_text_repel(data = indicators, aes(w_overshoot_Pos_error, overshoot_Pos_error, label = 'Overshoot')) +
  geom_segment(aes(x = 60, y = indicators$min_Pos_error, xend = 60, yend = indicators$max_Pos_error), arrow = arrow(length = unit(0.25, "cm"))) +
  geom_segment(aes(x = 60, y = indicators$max_Pos_error, xend = 60, yend = indicators$min_Pos_error), arrow = arrow(length = unit(0.25, "cm"))) +
  geom_text_repel(data = indicators, aes(60, indicators$min_Pos_error-0.2, label = 'Peak value')) +
  theme_minimal() + 
  theme(legend.position = 'none') + 
  ylab('Position error') +
  xlab('')


p_ret_pose


```





# Extension

This process is repeated in extension too.

```{r}

segment_region_length <- sum(segment$Region == 'Extending')



n_two_third_tail <- round(segment_region_length*2/3) 
n_first_quarter <- round(segment_region_length*1/4)

extension <- segment %>% 
                filter(Region == 'Extending') %>% 
                mutate(
                  Idx = 1:n(), tail_two_thirds =  ifelse(Idx < (n() - n_two_third_tail  ), FALSE, TRUE)
                  )
 
 

 ext_indicators <- extension %>%
                  describe(., return_location = TRUE)


```

```{r Current indicators in extension}

p_ext_cur <-  ggplot() + 
   geom_line(data = extension, aes(Idx, Current , colour = tail_two_thirds)) +
   geom_point(data = ext_indicators, aes(w_max_current, max_current)) + 
   geom_text_repel(data = ext_indicators, aes(w_max_current, max_current, label = 'Max')) +
   geom_point(data = ext_indicators, aes(w_max_current, max_current)) +
   geom_text_repel(data = ext_indicators, aes(w_min_current, min_current, label = 'Min')) +
   geom_point(data = ext_indicators, aes(w_min_current, min_current)) +
   geom_segment(aes(x = segment_region_length -n_two_third_tail   , y = ext_indicators$mean_current, xend = segment_region_length, yend = ext_indicators$mean_current)) + 
  geom_text_repel(data = ext_indicators, aes(segment_region_length - n_two_third_tail + 5.5 , mean_current - 0.035 , label = 'Mean')) + 
  geom_vline(xintercept = n_first_quarter, linetype = 'dashed' ) +
  geom_point(data = ext_indicators, aes(w_overshoot_current, overshoot_current)) +
  geom_text_repel(data = ext_indicators, aes(w_overshoot_current, overshoot_current, label = 'Overshoot')) +
  geom_segment(aes(x = 75, y = ext_indicators$min_current, xend = 75, yend = ext_indicators$max_current), arrow = arrow(length = unit(0.25, "cm"))) +
  geom_segment(aes(x = 75, y = ext_indicators$max_current, xend = 75, yend = ext_indicators$min_current), arrow = arrow(length = unit(0.25, "cm"))) +
  geom_text_repel(data = ext_indicators, aes(72, ext_indicators$min_current-0.05, label = 'Peak value')) +
  theme_minimal() + 
  theme(legend.position = 'none') + 
  xlab('')


p_ext_cur

```

```{r Pos error indicators in extension}

n_two_third_tail  <- round(segment_region_length*2/3) 
n_first_quarter <- round(segment_region_length*1/4)

p_ext_pos <-      ggplot() + 
                     geom_line(data = extension, aes(Idx, Pos_error , colour = tail_two_thirds)) +
                     geom_point(data = ext_indicators, aes(w_max_Pos_error, max_Pos_error)) + 
                     geom_text_repel(data = ext_indicators, aes(w_max_Pos_error, max_Pos_error, label = 'Max')) +
                     geom_point(data = ext_indicators, aes(w_max_Pos_error, max_Pos_error)) +
                     geom_text_repel(data = ext_indicators, aes(w_min_Pos_error, min_Pos_error, label = 'Min')) +
                     geom_point(data = ext_indicators, aes(w_min_Pos_error, min_Pos_error)) +
                     geom_segment(aes(x = segment_region_length - n_two_third_tail   , y = ext_indicators$mean_Pos_error, xend = segment_region_length, yend = ext_indicators$mean_Pos_error)) + 
                    geom_text_repel(data = ext_indicators, aes(segment_region_length - n_two_third_tail   +3, mean_Pos_error + 0.075, label = 'Mean')) + 
                    geom_vline(xintercept = n_first_quarter, linetype = 'dashed' ) +
                    geom_point(data = ext_indicators, aes(w_overshoot_Pos_error, overshoot_Pos_error)) +
                    geom_text_repel(data = ext_indicators, aes(w_overshoot_Pos_error, overshoot_Pos_error, label = 'Overshoot')) +
                    geom_segment(aes(x = 55, y = ext_indicators$min_Pos_error, xend = 55, yend = ext_indicators$max_Pos_error), arrow = arrow(length = unit(0.25, "cm"))) +
                    geom_segment(aes(x = 55, y = ext_indicators$max_Pos_error, xend = 55, yend = ext_indicators$min_Pos_error), arrow = arrow(length = unit(0.25, "cm"))) +
                    geom_text_repel(data = ext_indicators, aes(54, ext_indicators$min_Pos_error+1.45, label = 'Peak value')) +
                    theme_minimal() + 
                    theme(legend.position = 'none') + 
                    xlab('') +
                    ylab('Position error')

p_ext_pos

```


# All descriptors



```{r}

combined_plots <- cowplot::plot_grid(p_ret_cur, p_ret_pose, p_ext_cur , p_ext_pos, ncol = 2) # , labels = c('a)', 'b)', 'c)', 'd)')
combined_plots

combined_plots %>% 
  cowplot::save_plot(plot = .,
                     filename = here::here('figures', 'extracted_indicators.png'),
                     dpi = 450,
                     base_aspect_ratio = 2.7,
                     bg = 'transparent'
                     )


```


